---
title: "A knitr engine for maxima"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

# Description

<!-- README.md is generated from README.Rmd. Please edit that file -->

The R-package knitr already supports *many* programming languages to be used within code chunks. It also provides the possibility to write your own engine for processing code that is not supported. 

>Maxima is a system for the manipulation of symbolic and numerical expressions, including differentiation, integration, Taylor series, Laplace transforms, ordinary differential equations, systems of linear equations, polynomials, sets, lists, vectors, matrices and tensors. Maxima yields high precision numerical results by using exact fractions, arbitrary-precision integers and variable-precision floating-point numbers. Maxima can plot functions and data in two and three dimensions.

This engine can be used to process maxima code within Markdown documents. 

# Usage

To use it, one needs to register the function `maxima` in the file maxima.R as a knitr engine at the beginning of ones \*.Rmd file

```{r, eval = FALSE}
source("maxima.R")
knit_engines$set(maxima = maxima)
```

# Requirements

- `library(TexCheckR)`
- `library(data.table)`


# To Do

- printing certain matrices doesn't work, i.e. latex throws an error. This is because of TeX commands that fail in LaTeX
- chunk option eval doesn't have any effect
- using "%" to reuse the last command doesn't work
- putting lines breakes into the code chunk to avoid overflow of the echoed code chunk results in an maxima error
